NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-09 paper/Tables/2by2Table1.tex
regression table added

\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

>>>>

\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 CIs of the characteristics by BMI status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}

@@

\subsection{DM}\label{dm}

\caption{\label{tab:tab1DM}Weighted means, percentages, and 95 CIs of the characteristics by diabetic status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
\begin{tabular}[t]{lllllll}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Men (n = 2537)} & \multicolumn{3}{c}{Women (n = 3618)} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
  & Non-diabetes & Diabetes & P value\textsuperscript{*} & Non-diabetes & Diabetes & P value\\
Weighted prevalence (\%) & 94.1 (92.4, 95.4) & 5.9 (4.6, 7.6) &  & 96.4 (95.1, 97.4) & 3.6 (2.6, 4.9) & \\
Age (years) & 46.6 (45.2, 48.0) & 59.6 (55.6, 63.6) & < 0.001 & 48.7 (47.4, 50.0) & 60.2 (55.7, 64.7) & < 0.001\\
Country (\%) &  &  & 0.627 &  &  & 0.138\\
England & 83.8 (80.4, 86.7) & 79.0 (66.1, 87.9) &  & 84.9 (81.9, 87.4) & 81.2 (64.8, 91.0) & \\
Northern Ireland & 2.3 (1.3, 3.7) & 1.8 (0.2, 11.4) &  & 1.5 (0.9, 2.5) & 2.3 (2.2, 12.3) & \\
\hspace{1em}Scotland & 9.4 (7.0, 12.5) & 14.4 (7.0, 27.4) &  & 8.6 (6.4, 11.4) & 11.4 (3.6, 31.1) & \\
\hspace{1em}Wales & 4.6 (3.3, 6.3) & 4.8 (1.8, 12.3) &  & 5.1 (4.0, 6.4) & 2.0 (0.8, 5.2) & \\
Ethnicity (\%) &  &  & 0.267 &  &  & \\
\hspace{1em}White & 89.9 (86.9, 92.3) & 84.9 (71.9, 92.5) &  & 88.8 (85.8, 91.3) & 87.9 (73.1, 95.1) & \\
\hspace{1em}Non-white & 10.1 (7.7, 13.1) & 15.1 (7.5, 28.1) &  & 11.2 (8.7, 14.2) & 12.1 (4.9, 26.9) & \\
Education (\%) &  &  & 0.007 &  &  & 0.034\\
\hspace{1em}Degree or higher & 28.2 (24.9, 31.7) & 12.4 (6.2, 23.2) &  & 27.7 (24.8, 30.8) & 11.8 (4.7, 26.7) & \\
\hspace{1em}Lower than Degree & 71.8 (68.3, 75.1) & 87.6 (76.8, 93.8) &  & 72.3 (69.2, 75.2) & 88.2 (73.3, 95.3) & \\
Smoking status &  &  & 0.275 &  &  & 0.958\\
\hspace{1em}Current & 23.0 (19.9, 26.5) & 19.3 (10.6, 23.7) &  & 16.4 (14.3, 18.8) & 18.2 (8.3, 35.5) & \\
\hspace{1em}Ex-smoker & 24.5 (21.5, 27.8) & 34.5 (23.1, 47.9) &  & 23.8 (21.2, 26.7) & 23.5 (12.9, 38.8) & \\
\hspace{1em}Never & 52.5 (48.6, 56.3) & 46.2 (33.6, 59.3) &  & 59.7 (56.6, 62.8) & 58.3 (42.1, 72.9) & \\
activity (hours/day) \textsuperscript{\dag} & 1.53 (1.36, 1.71) & 1.07 (0.66, 1.59) & 0.094 & 0.76 (0.69, 0.84) & 0.38 (0.19, 0.60) & 0.002\\
BMI (kg/m2) & 27.3 (26.9, 27.6) & 30.1 (28.8, 31.3) & < 0.001 & 26.9 (26.5, 27.3) & 33.5 (31.7, 35.4) & < 0.001\\
WC (cm) & 96.9 (95.9, 97.9) & 108.5 (104.8, 112.3) & < 0.001 & 87.2 (86.3 88.1) & 107.1 (102.5, 111.8) & < 0.001\\
Carbohydrate eating patterns (\%) &  &  & 0.057 &  &  & 0.037\\
\hspace{1em}Low & 30.1 (26.8, 33.6) & 41.1 (29.2, 54.1) &  & 25.5 (22.8, 28.5) & 42.1 (27.1, 58.6) & \\
\hspace{1em}Moderate & 28.9 (25.4, 32.8) & 15.3 (8.3, 26.5) &  & 26.1 (23.0, 29.3) & 27.7 (15.9, 43.8) & \\
\hspace{1em}High & 41.0 (37.3, 44.7) & 43.6 (31.1, 57.0) &  & 48.4 (45.1, 51.7) & 30.2 (18.4, 45.3) & \\
Total energy intake (kJ) & 9016.8 (8806.8, 9226.8) & 8237.1 (7561.3, 8913.0) & 0.033 & 6844.2 (6715.9, 6972.5) & 5659.9 (5090.0, 6229.7) & < 0.001\\
Carbohydrate intake (g) & 257.7 (252.1, 263.3) & 236.8 (215.8, 257.8) & 0.062 & 199.8 (195.4, 204.3) & 163.9 (144.8, 183.0) & < 0.001\\
Glucose (mmol/l) & 5.23 (5.17, 5.28) & 9.35 (8.73, 10.03) & < 0.001 & 4.99 (4.96, 5.03) & 8.46 (7.69, 9.31) & < 0.001\\
A1C (\%) & 5.48 (5.45, 5.51) & 8.01 (7.68, 8.35) & < 0.001 & 5.47 (5.44, 5.49) & 7.68 (7.27, 8.11) & < 0.001\\
TC (mmol/l) & 4.79 (4.70, 4.88) & 4.14 (3.86, 4.44) & < 0.001 & 5.02 (4.95, 5.09) & 4.53 (4.12, 4.98) & < 0.001\\
HDL (mmol/l) & 1.24 (1.21, 1.27) & 1.05 (0.98, 1.13) & < 0.001 & 1.53 (1.50, 1.56) & 1.18 (1.06, 1.31) & < 0.001\\
LDL (mmol/l) & 2.86 (2.78, 2.94) & 2.16 (1.94, 2.40) & < 0.001 & 2.92 (2.87, 2.99) & 2.48 (2.12, 2.91) & < 0.001\\
TG (mmol/l) & 1.23 (1.18, 1.28) & 1.64 (1.41, 1.90) & < 0.001 & 0.99 (0.96, 1.02) & 1.46 (1.27, 1.68) & < 0.001\\
\multicolumn{7}{l}{\textit{Note: }}\\
\multicolumn{7}{l}{Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by diabetic status assessed using an F test (with Bonferroni correction to account for multiple testing across \$>\$ 2 groups)}\\
\multicolumn{7}{l}{for continuous variables or design-adjusted Pearson chi-square test}\\
\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the}\\
\multicolumn{7}{l}{survey.}\\

\subsection{Table 2 regressions in
survey}\label{table-2-regressions-in-survey}

\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
\begin{tabular}[t]{llllllllllll}
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Men (n = 2537)} & \multicolumn{6}{c}{Women (n = 3618)} \\
\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
Models & Low & Moderate & P value\textsuperscript{*} & High & P value & Models & Low & Moderate & P value & High & P value\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{Hypertension}}\\
\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{BMI}}\\
\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{WC}}\\
\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
\addlinespace[0.3em]
\multicolumn{12}{l}{\textbf{DM}}\\
\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
\multicolumn{12}{l}{\textit{Note: }}\\
\multicolumn{12}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}\\
\multicolumn{12}{l}{DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}\\
\multicolumn{12}{l}{\textsuperscript{*} P values were obtained from wald tests from either linear regression models or logistic regression models.}\\
\multicolumn{12}{l}{\textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}\\
\multicolumn{12}{l}{\textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}\\
\multicolumn{12}{l}{\textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}\\
\multicolumn{12}{l}{\textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}\\
\multicolumn{12}{l}{\textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}\\
\multicolumn{12}{l}{\textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}\\
\multicolumn{12}{l}{\textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG}\\
\multicolumn{12}{l}{(mmol/l);}\\
\multicolumn{12}{l}{\textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}\\

### 2018-08-09 paper/main.tex
some svyregress with BMI Waist
regression table added

\thesistitle{The time patterns of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\vspace*{.06\textheight}
{\scshape\huge \bfseries \univname\par}\vspace{1.5cm} % University name
\textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\Huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm] % Horizontal line

@@

\large \textit{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
%\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[2cm] % Research group name and department name

@@

%\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}

>>>>

\thesistitle{The time patterns of carbohydrate intake in UK adults -- the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\vspace*{.06\textheight}
{\scshape\LARGE \bfseries \univname\par}\vspace{1.5cm} % University name
\textsc{\Large MSc Project Report \\ 2017-2018}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\Huge \bfseries \ttitle\par}\vspace{0.3cm} % Thesis title
\HRule \\[1cm] % Horizontal line

@@

\large \textit{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
%\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[1.8cm] % Research group name and department name

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}
